Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-10 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Reviewer 2: Clarify which HOML

Adding the modal rules results in a calculus that is suitable for the basic modal logic \textbf{K}.
In other words, {\NDK} is sound and complete relative to {\ND} extended with axiom K ($\nec(A\imp B)\imp (\nec A\imp \nec B)$) and the necessitation rule (which establishes that $\nec A$ is a theorem if $A$ is a theorem).

>>>>

{\ND} is a calculus for a (non-modal) higher-order logic without 
functional and boolean extensionality principles \citep{BenzmuellerBrownKohlhase}.
Adding the modal rules results in a calculus that is suitable for a basic rigid modal logic \textbf{K}, in the sense that {\NDK} is sound and complete relative to {\ND} extended with axiom K ($\nec(A\imp B)\imp (\nec A\imp \nec B)$) and the necessitation rule (which establishes that $\nec A$ is a theorem if $A$ is a theorem).
